First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2020-01-08 MY_PUBLICATIONS/PRL/draft_v3/body.tex
updated draft 3

\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross 

@@

\includegraphics[scale=0.46]{../prl_plots/PRL_plot1.pdf}

@@

\noindent sections for each data set independently and were averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:

@@

@@

\indent For the recoil angles shown in Fig. \hyperref[fig:fig1]{1(a)-(c)}, all models agree and the cross sections are dominated by the PWIA up to $p_{r}\sim$300 MeV/c, which corresponds to the long-range part
of the NN-potential which is well understood. Beyond $p_{r}\sim$300 MeV/c, at recoil angles $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 model cross sections are dominated by
the PWIA and are within good agreement whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity to the different NN-potentials
at higher missing momenta. At recoil angles $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}] and $p_{r}>300$MeV/c, FSIs become dominant and exhibit a similar behaviour among all models which obscures any possibility
of extracting the momentum distributions at these angles. \\

@@

\indent The ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distributions (n$(p_{r})$) is shown in Fig. \ref{fig:fig2}. As a reference we selected the
deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.

@@

\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$. The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided. }

@@

\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], there is a clear onset of GEA at $p_{r}\gtrsim300$ MeV/c where FSI become dominant as indicated by the rise of FSI (solid lines) for
all theoretical calculations as compared to the reference. In this region, our experiment is statistically limited as we focused on kinematics at lower recoil angles where FSIs are small. The overlayed
Hall A data, however, shows excellent agreement with the Paris FSI. For $p_{r}<300$ MeV/c, FSIs are small as indicated by the approximate ratio R$\sim$1 for all the theoretical calculations using FSI, which the
data follows. The small dip observed in this region (R$<1$) is indicative of the approximate (not exact) cancellation between the PWIA/FSI interference (screening term) and the modulus-squared of FSI (re-scattering) terms in
the cross section. \\
\indent For $\theta_{nq}=45^{o}$ [Fig. \hyperref[fig:fig2]{2(b)}] at $p_{r}<300$ MeV/c, all theoretical calculations agree with each other and are sensitive to the momentum distribution inside the deuteron which
the data confirms. At $p_{r}\gtrsim300$ MeV/c, the Paris/AV18 calculations start to deviate from the CD-Bonn calculations, with the most substantial deviations observed at $p_{r}\sim 1$ GeV/c.
The CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim$580 MeV/c before FSIs start to dominate (R$>1$).
The data agrees well with the CD-Bonn PWIA calculation but show an earlier rise than predicted by the CD-Bonn FSI, a behaviour which is not described by any of the models. \\
\indent A similar behaviour is observed for $\theta_{nq}=35^{o}$ [Fig. \hyperref[fig:fig2]{2(a)}], where the CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c before being
overwhelmed by FSIs, whereas the Paris/AV18 calculations start to deviate from the CD-Bonn at $p_{r}\sim300$ MeV/c. The data shows sensitivity to CD-Bonn momentum distributions up to $p_{r}\sim$750 MeV/c before
exhibiting an earlier rise than predicted by CD-Bonn FSI. \\ 
\indent The $\theta_{nq}=35^{o}$ [Fig. \hyperref[fig:fig2]{2(a)}] appears to be the optimal kinematics to study the high momentum components of the deuteron wavefunction, as the data is sensitive to momentum
distributions up to $p_{r}\sim750$ MeV/c as compared to $p_{r}\sim$580 MeV/c for the $\theta_{nq}=45^{o}$ setting. \\

@@

The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn calculations
were found to be sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c for recoil angles $\theta_{nq}=35\pm5^{o}$, which the data agreed
up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.\\

>>>>

\indent  Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently
and were averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:

@@

\includegraphics[scale=0.5]{../prl_plots/PRL_plot1.pdf}

@@

@@

%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential. Above 300 MeV/c,
%corresponding to the medium and short range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in
%the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18. No model describes the data over the entire range--the data has a different shape than any of the models."

@@

\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq$300 MeV/c the cross sections are dominated by the PWIA and in agreement between all models.
The agreement at $p_{r}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP) is well known and commonly
used by modern potentials. \\
\indent Beyond $p_{r}\sim$300 MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
AV18 models significantly differ from the CD-Bonn. In this region, the Paris/AV18 are dominated by the PWIA and within good agreement of each other up $p_{r}\sim700$ MeV/c, while the CD-Bonn exhibits a completely different
behaviour where the cross sections are smaller and dominated by the PWIA up to $p_{r}\sim800$ MeV/c for $\theta_{nq}=35^{o}$ [Fig. \hyperref[fig:fig1]{1(a)}] and $p_{r}\sim580$ MeV/c for $\theta_{nq}=45^{o}$ [Fig. \hyperref[fig:fig1]{1(b)}].
The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant (original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18 groups
to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}] and $p_{r}>300$ MeV/c, FSIs become the dominant contributions to the cross sections for all models which exhibit a similar behaviour (smaller falloff) 
that overshadows any possibility of extracting the momentum distributions. \\

@@

%In plot 2: mention that the data disagrees with the AV18/Paris by about R = 2.5.  Also note that since we understand how FSIs work from th_nq= 75 deg,  FSIs should be well understood at the 35 and 45 deg settings.
\indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distributions ($\sigma^{\text{CD-Bonn PWIA}}_{red}$) is shown in Fig. \ref{fig:fig2}.
As a reference we selected the deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.

@@

\caption{The ratio R($p_{r}$) = $\sigma_{red}/\sigma^{{\text{CD-Bonn PWIA}}}_{red}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}

@@

\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig2]{2(a),(b)}] the data is best described by the CD-Bonn PWIA calculation for recoil momenta up to $p_{r}\sim700$ MeV/c and $\sim580$ MeV/c, respectively.
Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic region where recoil angles are small and FSIs are reduced.
At larger recoil momenta where the ratio is $R>1$, FSIs dominate the cross section models and the data is not well described by any of the models. This behaviour of the data is not well understood
and additional data on this statistically limited region would be required before any conclusions can be made. \\
\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], the FSIs are small below $p_{r}\sim$300 MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
At $p_{r}>300$ MeV/c, the data was statistically limited as our focus was on the smaller recoil angles. The Hall A data, however, shows a reasonable agreement with the FSIs from all models which gives us confidence in our understanding
of FSIs at the smaller recoil angles. This opens a question on whether there might be additional effects needed in the CD-Bonn model that would account for the discrepancy between data and CD-Bonn FSI at smaller angles. \\

@@

The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn model was found to be
significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{r}$.
At higher missing momentum, however, all models were unable to describe the data. In addition, at these large momentum settings statistical limitations were encountered as well.\\

### 2020-01-08 MY_PUBLICATIONS/PRL/draft_v3/introduction.tex
updated draft 3

\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)\cite{sargsian_2015} have helped quantify the contributions from FSIs, MECs and ICs on

>>>>

\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)[See Section 5 of Ref. \cite{sargsian_2015}] have helped quantify the contributions from FSIs, MECs and ICs on
